Distributed Version Control Systems

### 2010-04-27 paper.tex
Agregue algunas cositas en todas las secciones. Casi como que esta para entregarlo como primera iteracion

%----------------------------------------------------------------------
% Title Information, Abstract and Keywords
%----------------------------------------------------------------------
\title[Investigation on GIT]{%
       Investigation on GIT}

% format author this way for journal articles.
% MAKE SURE THERE ARE NO SPACES BEFORE A \member OR \authorinfo
% COMMAND (this also means `don't break the line before these
% commands).
\author[GRUPOAPIT]{Damian Alonso,%
\and{} Bruno Bonnano
\and{} Nicol\'{a}s Calligaro
\and{}and Nicol\'{a}s Perez Santoro
}

@@

The concept of distributed repositories came up first on the commercial product 
Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
on to design BitKeeper, another commercial VCS which expanded on those ideas. 
BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
the license to use BitKeeper was finished. 
To replace the use of BitKeeper in the Linux kernel, two projects started, Git and 
Mercurial, both now mature DVCS. Other open source DVCS in use today are Bazaar, 
developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
the idea of tracking only patches and not versions.

@@

Ejemplo de cita \cite{linusgit}

@@

\subsection{Atomic Commits}

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
change, since commits are made in the local repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.

@@

Centralized VCS's like Subversion makes certain copies through history called tags. But on Git we have more tools, one of them is that we can have an arbitrary description attached in the tag, in fact, you can store the whole release announcements here. Moreover, as with the commit, is stored the identity of who made the tag and this identity can be verified if we add a cryptographically PGP sign to the tag

@@

Merge on Git between branches is great!, all the history of both branches is preserved over the merges.
When we make a merge we have two scenarios:
Fast-forward merge: we refer to this when the changes only was made on only one of the branches, they are simply replayed on the other branch.
Three-way merge: When changes exists on both branches, they are merged and git will report any conflict and let you resolve them.

\subsection{Pushing and fetching/pulling}

When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
Push refers to taking all my changes and add them to the repository of another co-worker. But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, instead it, we make Push in a "central repository" where all team make their Pushes too, this logic is similar to traditional VCS, but we need to keep in mind that we could have a lot of "central repositorys" for different parts of our project.
Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
At the same way, another co-worker can do Pull over my working copy and get my new code & changes without any problem.

@@

Explicar los casos donde resulta interesante aplicar esta herramienta. 
También la idea es mostrar configuraciones posibles para la empresa donde 
se vea la forma de hacer cosas que con un sistema no distribuido no sería 
posible, o como es posible hacer lo mismo que se podía hacer con svn 
(usando un repositorio que tenga el branch principal), de manera que 
no te limita.

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
\section{Then, why should I use it in my project?}

Explicar los casos donde resulta interesante aplicar esta herramienta. 
También la idea es mostrar configuraciones posibles para la empresa donde 
se vea la forma de hacer cosas que con un sistema no distribuido no sería 
posible, o como es posible hacer lo mismo que se podía hacer con svn 
(usando un repositorio que tenga el branch principal), de manera que 
no te limita.

@@

\bibitem{linusgit}
Linus Torvalds
\newblock Google Talk presentation on Git

>>>>

%----------------------------------------------------------------------
% Title Information, Abstract and Keywords
%----------------------------------------------------------------------
\title[Distributed Version Control Systems]{%
       Distributed Version Control Systems}

% format author this way for journal articles.
% MAKE SURE THERE ARE NO SPACES BEFORE A \member OR \authorinfo
% COMMAND (this also means `don't break the line before these
% commands).
\author[GRUPOAPIT]{Damian Alonso,
\and{} Bruno Bonnano,
\and{} Nicol\'{a}s Calligaro
\and{}and Nicol\'{a}s Perez Santoro
}

@@

The concept of distributed repositories came up first on the commercial product 
Sun TeamWare (\emph{good citation needed}), designed by Larry McVoy who later went 
on to design BitKeeper, another commercial VCS which expanded on those ideas. 
BitKeeper was used from 2002 to 2005 to manage the Linux kernel source until 
the license to use BitKeeper was finished. 
To replace the use of BitKeeper in the Linux kernel, two projects started, Git (by
Linus Torvalds \cite{linusgit} and 
Mercurial, both now mature DVCS. Other open source DVCS in use today are Bazaar, 
developed by Canonical Ltd. and used to maintain the Ubuntu codebase, and Darcs, based on 
the idea of tracking only patches and not versions.

@@

%Ejemplo de cita \cite{linusgit}

@@

\subsection{More Atomical Commits}

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
change, since commits are made in the local repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes. 
Many little commits, if needed, can be grouped as a bigger, conceptual commit.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions
(this also makes commits easier).

%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.

@@

Centralized VCS's like Subversion makes certain copies through history called tags. 
But on Git we have more tools, one of them is that we can have an arbitrary 
description attached in the tag, in fact, you can store the whole release announcements here. 
Moreover, as with the commit, is stored the identity of who made the tag and this identity 
can be verified if we add a cryptographically PGP sign to the tag.

@@

Merge on Git between branches is greatly improved over, say, SVN, because all the history of 
both branches is preserved over the merges.
When we make a merge we have two scenarios:
Fast-forward merge: we refer to this when the changes only was made on only one of the branches,
they are simply replayed on the other branch.
Three-way merge: When changes exists on both branches, they are merged and git will report any 
conflict and let you resolve them.

\subsection{Pushing and pulling}

% comentario via nps: cambié ``co-worker'' por ``peer'' porque es más neutral
When we want to share our work with the rest of the team we have two basic concepts, 
\emph{push} and \emph{pull}.
Push refers to taking all my changes and add them to the repository of another peer. 
But in practice we don't do this becouse we shouldn't make a push on a peer working copy, 
instead it, we push in a ``central repository'' where all the team make their pushes too, 
this logic is similar to traditional VCS, but we need to keep in mind that we could have a 
lot of ``central repositories'' for different parts of our project.
Pull is a composite action of ``fetch'' and ``merge'', fetching takes the changes from selected 
repository of a peer and copies them to a local repository, and 
then those changes are merged with the sourcecode of my local repository.
In the same way, another peer can pull on my working copy and get my code and 
changes without any problem.

If you work against a central repository, pulling and pushing do look very much like
the idea of checking out and checking in, but that's the only way of working in a centralized VCS.
In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
read-only mode (via ssh, http, or just sharing the directory) to let other people pull from them.

@@

As mentioned before, this tool allows for differents workflows that just weren't 
possible before.

Changes can be just shared between peers, without needing to access the central 
repository. Branches can be created instantly, and merging them is easier since 
the whole history of changesets is preserved instead of just taking the diff of 
the versions.

Push and pull are much more versatile than checking in and out, since you can push 
changes into many repositories and pull from many others, not just a central one.
In fact, there is no need to push at all:
everyone could be just pulling changes from each other. For example, two co-workers could work 
in a feature, pulling from each other, then let a third one fetch them and do a code review, and then 
discard it or merge it. A fourth could fetch all reviewed changes into a test version, to do an 
acceptance test, and then merge the changes into a final version.

%Explicar los casos donde resulta interesante aplicar esta herramienta. 
%También la idea es mostrar configuraciones posibles para la empresa donde 
%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
%posible, o como es posible hacer lo mismo que se podía hacer con svn 
%(usando un repositorio que tenga el branch principal), de manera que 
%no te limita.

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
\section{Then, why should I use it in my project?}
Does everybody need these features? Speed, offline working, 
and easyness of branching/merging are nice features even if you work simply pulling 
and pushing changes against a central repository and not every peer out there. In some 
projects and with some tools, the advantage of going distributed may not be clear. 
For starters, in many closed source projects there is no need nor desire to have anything
other than centralized repositories, and while you can use a DVCS with a centralized
repository, there may not be enough to gain to balance the cost of changing. Distributed 
versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need 
(even for one person proyects, Git and Mercurial may be easier to use than SVN).
Centralized VCS also have their advantages, you don't need to have the whole history in your 
personal repository so you can save space, for example in Perforce you can check out only a part of the 
repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
without getting a performance hit on some operations\cite{linusgit}.

%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
% siempre desde el punto de vista "closed source" (debatible).

@@

\bibitem{linusgit}
Linus Torvalds
\newblock \emph{Google Talk presentation on Git}

\bibitem{perforceclientspec}
Perforce documentation on ``Editing Client Specs''

\newblock \emph{
http://www.perforce.com/perforce/doc.current/manuals/p4web
/help/editclient.html
}
